\paperTitle

### 2014-01-31 doc/icml2014/directed.tex
Udpdated examples (non-example) section

\todo{somewhere give examples that are not in our class, preferably the simplest one - noisy-or, cite Sontag}

@@

@@

@@

\begin{figure}
  \centering
  \subfigure[Hidden Markov Model] {
    \includegraphics[width=0.45\columnwidth]{figures/hmm.pdf}
    \label{fig:examples-hmm}
  }
%  \subfigure[Directed grid model] {
%    \label{fig:examples-grid}
%    \includegraphics{figures/grid.pdf}
%  }
  \subfigure[Tree model] {
    \includegraphics[width=0.45\columnwidth]{figures/tree.pdf}
    \label{fig:examples-tree}
  }
  \caption{Examples of directed models satisfying the exclusive views property.}
  \label{fig:examples}
\end{figure}

>>>>

@@

\begin{figure}
  \centering
  \subfigure[Hidden Markov Model] {
    \includegraphics[width=0.45\columnwidth]{figures/hmm.pdf}
    \label{fig:examples-hmm}
  }
%  \subfigure[Directed grid model] {
%    \label{fig:examples-grid}
%    \includegraphics{figures/grid.pdf}
%  }
  \subfigure[Tree model] {
    \includegraphics[width=0.45\columnwidth]{figures/tree.pdf}
    \label{fig:examples-tree}
  }
  \subfigure[Non-example: a noisy-or network] {
    \includegraphics[height=5em]{figures/non-example.pdf}
    \label{fig:examples-noisy-or}
  }
  \caption{}
  \label{fig:examples}
\end{figure}

@@

\paragraph{Non-examples}
\label{sec:non-example}

The simplest example of a model not identifiable by our algorithm is
  a mixture model with a single view, i.e. \figureref{three-view} with
  just the variables $h_1$ and $x_1$.
However, without further assumptions the model itself is not
  identifiable\footnote{To see this, observe that the probability-mass
  can be arbitrarily exchanged between $\Pr(h_1)$ and $\Pr(x_1 | h_1)$}.
A class of binary-valued noisy-or networks which do not possess the
  bottleneck property are be shown to be identifiable by
  \citet{halpern13noisyor}; 
\figureref{examples-noisy-or} presents one example in this class.

@@
